Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Better formatting, more shit

\lstdefinestyle{Matlab}{
  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
  showstringspaces=false,stringstyle=\color{mylilas},
}

>>>>

\lstdefinestyle{Matlab}{
  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
  commentstyle=\color{mygreen}\slshape,emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
  keywordstyle=[2]{\color{black}},keywordstyle={\color{blue}\bfseries},language=Matlab,literate={~} {\texttildelow}{1},
  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=1em,numberstyle=\footnotesize,
  showstringspaces=false,stringstyle=\color{mylilas},xleftmargin=1em,
}
